\chapter*{Useful Texts \& Further Readings}

\section*{String Theory}
\begin{itemize}
    \item Polchinski, J., \textit{String theory: Volumes 1\& 2, an introduction to the bosonic string}, Cambridge university press, (1998).
    \item Green, M. B., Schwarz, J. H., \& Witten, E., \textit{Superstring theory: volume 2, loop amplitudes, anomalies and phenomenology}, Cambridge university press, (2012).
    \item Zwiebach, B., \textit{A first course in string theory}, Cambridge university press, (2004).
    \item Kiritsis, E., \textit{String theory in a nutshell} (Vol. 9), Princeton University Press, (2011).
    \item Ried-Edwards, R. A., \textit{String Theory Lectures}, taught at Cambridge (2019), available via \href{http://www.damtp.cam.ac.uk/people/rar31/LectureNotes.pdf}{http://www.damtp.cam.ac.uk/people/rar31/LectureNotes.pdf}.
\end{itemize}

\section*{Conformal Field Theory}
\begin{itemize}
    \item Blumenhagen, R., \& Plauschinn, E., \textit{Introduction to conformal field theory: with applications to string theory} (Vol. 779), Springer Science \& Business Media, (2009).
    \item Francesco, P., Mathieu, P., \& Sénéchal, D., \textit{Conformal field theory}, Springer Science \& Business Media, (2012).
    \item Qualls, J. D., \textit{Lectures On Confromal Field Theory}, (2016), available via \\
    \href{https://arxiv.org/pdf/1511.04074.pdf}{https://arxiv.org/pdf/1511.04074.pdf}.
\end{itemize}

\section*{Quantum Field Theory}
\begin{itemize}
    \item  Zee A., \textit{Quantum field theory in a nutshell}, Second Edition, Princeton university press, 2010.
    \item Peskin M. E. \& Schroeder D. V., \textit{An introduction to quantum field theory}, CRC Press
\end{itemize}

\section*{Miscellaneous}
\begin{itemize}
    \item Goddard, P., \& Olive, D., \textit{Kac-Moody and Virasoro algebras in relation to quantum physics}, International Journal of Modern Physics A, 1(02), 303-414, (1986).
\end{itemize}